---
title: "Second Stage"
date: '2022-07-15'
output:
  pdf_document:
    keep_tex: yes
    latex_engine: xelatex
    number_sections: yes
    toc: yes
    toc_depth: 2

header-includes:
- \usepackage{graphicx}
- \usepackage{float}
- \usepackage{amsmath}
- \usepackage{longtable}
- \usepackage{dcolumn} 
---

```{r setup, include=FALSE,warning=FALSE}
knitr::opts_chunk$set(echo = FALSE,message = FALSE)
# load data
d = read.csv("0604newdata.csv")

# load packages
library(tidyverse)
library(summarytools)
library(prettyR)
library(modelsummary)
library(reshape2)
library(sjPlot)
library(hrbrthemes)
library(likert)
library(stargazer)
library(lavaan)
library(kableExtra)
library(psych)
library(corrplot)
library(ggbiplot)
library(tinytex)

#age
d = d %>%
  mutate(age = ifelse(Q1>100,2022-Q1,Q1))

d = d %>%
  dplyr:: mutate(gender = Q2, 
         education = Q6,
         income = Q7)

#calculate depression socre
d = d %>%
  rowwise() %>%
  dplyr:: mutate(depre = sum(c_across(Q24_1:Q24_9)))

# rename media use
d = d %>%
  dplyr:: mutate(Use_phone = Q15_1,
         Socialmedia_chat = Q15_2,
         Socialmedia_post = Q15_3,
         Socialmedia_scan = Q15_4,
         Socialmedia_news = Q15_5,
         Online_search = Q15_6,
         Email = Q15_7,
         Media_share = Q15_8,
        Short_message = Q15_9,
        Digital_game = Q15_10,
        Whatsapp_wechat_line = Q15_11,
        Skype_FT_zoom = Q15_12,
        Online_friends = Q15_13,
        Phone_call = Q15_14,
        Watch_TV = Q15_5,
        Radio = Q15_6,
        Newspaper = Q15_17)

```

\newpage

## PCA of Prevention Behaviors

The figure suggests that prevention behaviors cannot be well categorized automatically.

```{r PCA plot, echo=FALSE,fig.asp=0.95}

d %>% 
  select(Q18_1:Q18_16) %>%
  prcomp(,scale = TRUE) %>%
  plot(, type = "l")
  

```

\newpage

### Correlations between Prevention Behaviors

The figure suggests the strong correlations exist between prevention behavior items.

```{r echo=FALSE,fig.asp = .92}

d %>%
  select(Q18_1:Q18_16) %>%
  cor() %>%
  corrplot(., method = 'number')
```

## Manual Categorization of Prevention Behaviors

-   Select Q18_8 Cover mouth when cough; Q18_15 Help family members and friends; Q18_16 Care about elders as other-oriented/social-oriented prevention behaviors

-   Select the rest variables as self-oriented prevention behaviors

    ```{r regression table}
    #rename variables
    d =d %>%
      mutate(gender = Q2, 
             education = Q6,
             income = Q7)

    #self-oriented prevention behaviors
    d$mean_selfnew  = d  %>%
      rowwise() %>%
      select(Q18_1:Q18_7,Q18_9:Q18_14) %>%
      dplyr:: mutate(mean_self = mean(c_across(Q18_1:Q18_14))) %>%
      pull(.,mean_self)

    # social-oriented prevvention behaviors
    d = d %>%
      rowwise() %>%
      dplyr::mutate(mean_social = sum(Q18_8+Q18_15+Q18_16)/3)


    # calculate empathy

    d$Q27_1 = as.numeric(d$Q27_1)
    d$Q27_2 = as.numeric(d$Q27_2)
    d$Q27_3 = as.numeric(d$Q27_3)  

    d = d %>%
      mutate(empathy = (Q27_1 + Q27_2 + Q27_3)/3) 

    # reg 

    re_self = lm(mean_selfnew ~ empathy+age +gender + education +income,data = d) 

    re_social = lm(mean_social ~ empathy +age +gender + education +income,data = d)


    stargazer(re_self,re_social,
              type = "text",
              intercept.bottom = T,
              ci = F, digits=2,
              notes = "Empathy on self/social oriented prevention",
              model.names = T,
              single.row = T)

    ```

## Relationship between social support, resilience and life satisfaction

```{r echo=FALSE, warning=FALSE}

#rename variables
d =d %>%
  mutate(gender = Q2, 
         education = Q6,
         income = Q7)

# recode resilience
d = d %>%
  mutate(re1_po = Q25_1,
         re1_ng = Q25_2,
         re2_po = Q25_3,
         re2_ng = Q25_4,
         re3_po = Q25_5,
         re3_ng = Q25_6) %>%
  mutate_if(is.integer, as.numeric) %>%
  mutate_at(c("re1_ng","re2_ng","re3_ng") ,
            funs(dplyr::recode(.,
                           "1" = 7,
                           "2" =6,
                          "3" =5,
                           "4"=4,
                          "5"=3,
                          "6"=2,
                          "7"=1))) 

# calculate mean_resilience
d= d %>%
  as_tibble()%>% 
  rowwise()%>%
  dplyr:: mutate(mean_resilience = sum(c_across(re1_po:re3_ng))/6)


## Support calculation
d= d %>%
  as_tibble()%>%
  rowwise()%>%
  dplyr:: mutate(mean_support = sum(c_across(Q26_1:Q26_6))/6)

# regression of satisfaction Q23

re_sat1 = lm(Q23 ~ mean_support + mean_resilience,data = d) 

re_sat2 = lm(Q23 ~ mean_support + mean_resilience + age + gender + education + income,data = d)


stargazer(re_sat1,re_sat2,
          type = "text",
          intercept.bottom = T,
          dep.var.labels= "life satisfaction",
          ci = F, digits=2,
          notes = "Social support, resilience and life satisfaction",
          model.names = T,
          single.row = T)






```

## Relationships between demographic variables, media use, information-source assessment and depression

```{r echo=FALSE,results='asis'}
library("rmarkdown")
library("tinytex")
library("stargazer")
library("sandwich")

#calculate depression socre
d = d %>%
  rowwise() %>%
  dplyr:: mutate(depre = sum(c_across(Q24_1:Q24_9)))

#rename variables
d = d %>%
  dplyr:: mutate(gender = Q2, 
         education = Q6,
         income = Q7)


# Demographic variables and depression Q24
## Demographics separately on Depression
rd1 = lm(depre ~ age, data = d)
rd2 = lm(depre ~ gender, data = d)
rd3 = lm(depre ~ education, data = d)
rd4 = lm(depre ~ income, data = d)

stargazer(rd1,rd2,rd3,rd4,
          type="latex",
          float = TRUE,
          font.size = "small",
          align = TRUE,
          intercept.bottom = T,
           dep.var.labels= "Depression",
          ci = F, digits=2,
          notes = "Demographics separately on Depression",
          column.sep.width = "-25pt", 
          model.names = T,
          single.row = T,
          no.space = TRUE)

# All demographics and depression
rd5 = lm(depre ~ age +gender + education +income, data = d)

stargazer(rd5,
          type="latex",
          float = TRUE,
          font.size = "small",
          align = TRUE,
          intercept.bottom = T,
           dep.var.labels= "Depression",
          ci = F, digits=2,
          notes = "All demographicson and Depression",
          column.sep.width = "0.1pt", 
          model.names = T,
          single.row = T,
          no.space = TRUE)

```

## Mediation effects of media use

### Mediation of phone use

No significant mediation effect.

```{r}


#use phone

usephone.mod = '
  depre ~ a1* Use_phone +b1 *age + b2*gender +b3*education + b4* income
  Use_phone~ c1 *age + c2*gender +c3*education + c4* income
  Indirect1 := a1*c1
  Indirect2 := a1*c2
  Indirect3 := a1*c3
  Indirect4 := a1*c4
  age ~~ gender
  gender ~~ education
  education ~~ income
  age ~~ education
  age ~~ income
  gender ~~ income'

usephone.model = sem(usephone.mod, data = d,
                    std.lv = TRUE , meanstructure = TRUE )

parameterestimates(usephone.model, boot.ci.type = "bca.simple", standardized = TRUE) %>% 
  kbl(.,booktab = TRUE) %>%
  kable_styling(latex_options = c("hold_position")) 


```

\newpage

### Mediation of social media chat

Social media chat has mediation effect between age and depression.

```{r}

# social media chat
smc.mod = '
  depre ~ a1* Socialmedia_chat +b1 *age + b2*gender +b3*education + b4* income
  Socialmedia_chat~ c1 *age + c2*gender +c3*education + c4* income
  Indirect1 := a1*c1
  Indirect2 := a1*c2
  Indirect3 := a1*c3
  Indirect4 := a1*c4
  age ~~ gender
  gender ~~ education
  education ~~ income
  age ~~ education
  age ~~ income
  gender ~~ income'
smc.model = sem(smc.mod, data = d,
                     std.lv = TRUE , meanstructure = TRUE )

parameterestimates(smc.model, boot.ci.type = "bca.simple", standardized = TRUE) %>% 
  kbl(.,booktab = TRUE) %>%
  kable_styling(latex_options = c("hold_position")) 
```

\newpage

### Mediation of Social media Post

Social media post has mediation effects between age, education and depression.

```{r}
smp.mod = '
  depre ~ a1* Socialmedia_post +b1 *age + b2*gender +b3*education + b4* income
  Socialmedia_post~ c1 *age + c2*gender +c3*education + c4* income
  Indirect1 := a1*c1
  Indirect2 := a1*c2
  Indirect3 := a1*c3
  Indirect4 := a1*c4
  age ~~ gender
  gender ~~ education
  education ~~ income
  age ~~ education
  age ~~ income
  gender ~~ income'
smp.model = sem(smp.mod, data = d,
                std.lv = TRUE , meanstructure = TRUE )

parameterestimates(smp.model, boot.ci.type = "bca.simple", standardized = TRUE) %>% 
  kbl(.,booktab = TRUE) %>%
  kable_styling(latex_options = c("hold_position")) 

```

\newpage

### Mediation of Social media News

Social media use has mediation effects between age and depression.

```{r}
smn.mod = '
  depre ~ a1* Socialmedia_news +b1 *age + b2*gender +b3*education + b4* income
  Socialmedia_news~ c1 *age + c2*gender +c3*education + c4* income
  Indirect1 := a1*c1
  Indirect2 := a1*c2
  Indirect3 := a1*c3
  Indirect4 := a1*c4
  age ~~ gender
  gender ~~ education
  education ~~ income
  age ~~ education
  age ~~ income
  gender ~~ income'
smn.model = sem(smn.mod, data = d,
                std.lv = TRUE , meanstructure = TRUE )

parameterestimates(smn.model, boot.ci.type = "bca.simple", standardized = TRUE) %>% 
  kbl(.,booktab = TRUE) %>%
  kable_styling(latex_options = c("hold_position")) 

```

\newpage

### Mediation of Online Search

Online search has mediation effect between age and depression.

```{r}
os.mod = '

  depre ~ a1* Online_search +b1 *age + b2*gender +b3*education + b4* income

  Online_search~ c1 *age + c2*gender +c3*education + c4* income

  Indirect1 := a1*c1

  Indirect2 := a1*c2

  Indirect3 := a1*c3

  Indirect4 := a1*c4

  age ~~ gender

  gender ~~ education

  education ~~ income

  age ~~ education

  age ~~ income

  gender ~~ income'

os.model = sem(os.mod, data = d,

                std.lv = TRUE , meanstructure = TRUE )

parameterestimates(os.model, boot.ci.type = "bca.simple", standardized = TRUE) %>% 

  kbl(.,booktab = TRUE) %>%

  kable_styling(latex_options = c("hold_position"))

```

\newpage

### Mediation of Email

Email has mediation effect between age and depression.

```{r}
eml.mod = '
  depre ~ a1* Email +b1 *age + b2*gender +b3*education + b4* income
  Email~ c1 *age + c2*gender +c3*education + c4* income
  Indirect1 := a1*c1
  Indirect2 := a1*c2
  Indirect3 := a1*c3
  Indirect4 := a1*c4
  age ~~ gender
  gender ~~ education
  education ~~ income
  age ~~ education
  age ~~ income
  gender ~~ income'
eml.model = sem(eml.mod, data = d,
               std.lv = TRUE , meanstructure = TRUE )

parameterestimates(eml.model, boot.ci.type = "bca.simple", standardized = TRUE) %>% 
  kbl(.,booktab = TRUE) %>%
  kable_styling(latex_options = c("hold_position")) 
```

### Mediation of media share

Media share has mediation effects between age, education and depression.

```{r}
ms.mod = '
  depre ~ a1* Media_share +b1 *age + b2*gender +b3*education + b4* income
  Media_share~ c1 *age + c2*gender +c3*education + c4* income
  Indirect1 := a1*c1
  Indirect2 := a1*c2
  Indirect3 := a1*c3
  Indirect4 := a1*c4
  age ~~ gender
  gender ~~ education
  education ~~ income
  age ~~ education
  age ~~ income
  gender ~~ income'
ms.model = sem(ms.mod, data = d,
                std.lv = TRUE , meanstructure = TRUE )

parameterestimates(ms.model, boot.ci.type = "bca.simple", standardized = TRUE) %>% 
  kbl(.,booktab = TRUE) %>%
  kable_styling(latex_options = c("hold_position")) 
```

\newpage

### Mediation of Short message

Short message has mediation effect between age and depression.

```{r}
smg.mod = '
  depre ~ a1* Short_message +b1 *age + b2*gender +b3*education + b4* income
  Short_message~ c1 *age + c2*gender +c3*education + c4* income
  Indirect1 := a1*c1
  Indirect2 := a1*c2
  Indirect3 := a1*c3
  Indirect4 := a1*c4
  age ~~ gender
  gender ~~ education
  education ~~ income
  age ~~ education
  age ~~ income
  gender ~~ income'
smg.model = sem(smg.mod, data = d,
               std.lv = TRUE , meanstructure = TRUE )

parameterestimates(smg.model, boot.ci.type = "bca.simple", standardized = TRUE) %>% 
  kbl(.,booktab = TRUE) %>%
  kable_styling(latex_options = c("hold_position")) 

```

\newpage

### Mediation of Digital Game

Digital game has mediation effect between age and depression.

```{r}
dg.mod = '
  depre ~ a1* Digital_game +b1 *age + b2*gender +b3*education + b4* income
  Digital_game~ c1 *age + c2*gender +c3*education + c4* income
  Indirect1 := a1*c1
  Indirect2 := a1*c2
  Indirect3 := a1*c3
  Indirect4 := a1*c4
  age ~~ gender
  gender ~~ education
  education ~~ income
  age ~~ education
  age ~~ income
  gender ~~ income'
dg.model = sem(dg.mod, data = d,
                std.lv = TRUE , meanstructure = TRUE )

parameterestimates(dg.model, boot.ci.type = "bca.simple", standardized = TRUE) %>% 
  kbl(.,booktab = TRUE) %>%
  kable_styling(latex_options = c("hold_position")) 

```

\newpage

### Mediation of Whatsapp

Whatsapp has mediation effects between age, education and depression.

```{r}
wapp.mod = '
  depre ~ a1* Whatsapp_wechat_line +b1 *age + b2*gender +b3*education + b4* income
  Whatsapp_wechat_line~ c1 *age + c2*gender +c3*education + c4* income
  Indirect1 := a1*c1
  Indirect2 := a1*c2
  Indirect3 := a1*c3
  Indirect4 := a1*c4
  age ~~ gender
  gender ~~ education
  education ~~ income
  age ~~ education
  age ~~ income
  gender ~~ income'
wapp.model = sem(wapp.mod, data = d,
               std.lv = TRUE , meanstructure = TRUE )

parameterestimates(wapp.model, boot.ci.type = "bca.simple", standardized = TRUE) %>% 
  kbl(.,booktab = TRUE) %>%
  kable_styling(latex_options = c("hold_position")) 
```

\newpage

###  Mediation of Skype

Skype has mediation effects between age, education, income and depression.

```{r}
sky.mod = '
  depre ~ a1* Skype_FT_zoom +b1 *age + b2*gender +b3*education + b4* income
  Skype_FT_zoom~ c1 *age + c2*gender +c3*education + c4* income
  Indirect1 := a1*c1
  Indirect2 := a1*c2
  Indirect3 := a1*c3
  Indirect4 := a1*c4
  age ~~ gender
  gender ~~ education
  education ~~ income
  age ~~ education
  age ~~ income
  gender ~~ income'
sky.model = sem(sky.mod, data = d,
                 std.lv = TRUE , meanstructure = TRUE )

parameterestimates(sky.model, boot.ci.type = "bca.simple", standardized = TRUE) %>% 
  kbl(.,booktab = TRUE) %>%
  kable_styling(latex_options = c("hold_position")) 
```

\newpage

###  Mediation of Online friends

Online friends has mediation effects between age, education and depression.

```{r}
of.mod = '
  depre ~ a1* Online_friends +b1 *age + b2*gender +b3*education + b4* income
  Online_friends ~ c1 *age + c2*gender +c3*education + c4* income
  Indirect1 := a1*c1
  Indirect2 := a1*c2
  Indirect3 := a1*c3
  Indirect4 := a1*c4
  age ~~ gender
  gender ~~ education
  education ~~ income
  age ~~ education
  age ~~ income
  gender ~~ income'
of.model = sem(of.mod, data = d,
                std.lv = TRUE , meanstructure = TRUE )

parameterestimates(of.model, boot.ci.type = "bca.simple", standardized = TRUE) %>% 
  kbl(.,booktab = TRUE) %>%
  kable_styling(latex_options = c("hold_position")) 
```

\newpage

### Mediation of Watch TV

TV has mediation effect between age and depression.

```{r}
TV.mod = '
  depre ~ a1* Watch_TV +b1 *age + b2*gender +b3*education + b4* income
  Watch_TV ~ c1 *age + c2*gender +c3*education + c4* income
  Indirect1 := a1*c1
  Indirect2 := a1*c2
  Indirect3 := a1*c3
  Indirect4 := a1*c4
  age ~~ gender
  gender ~~ education
  education ~~ income
  age ~~ education
  age ~~ income
  gender ~~ income'
TV.model = sem(TV.mod, data = d,
               std.lv = TRUE , meanstructure = TRUE )

parameterestimates(TV.model, boot.ci.type = "bca.simple", standardized = TRUE) %>% 
  kbl(.,booktab = TRUE) %>%
  kable_styling(latex_options = c("hold_position")) 
```

\newpage

### Mediation of Radio

Radio has mediation effect between age and depression.

```{r}
Rd.mod = '
  depre ~ a1* Radio +b1 *age + b2*gender +b3*education + b4* income
  Radio~ c1 *age + c2*gender +c3*education + c4* income
  Indirect1 := a1*c1
  Indirect2 := a1*c2
  Indirect3 := a1*c3
  Indirect4 := a1*c4
  age ~~ gender
  gender ~~ education
  education ~~ income
  age ~~ education
  age ~~ income
  gender ~~ income'
Rd.model = sem(Rd.mod, data = d,
               std.lv = TRUE , meanstructure = TRUE )

parameterestimates(Rd.model, boot.ci.type = "bca.simple", standardized = TRUE) %>% 
  kbl(.,booktab = TRUE) %>%
  kable_styling(latex_options = c("hold_position")) 
```

\newpage

### Mediation of newspaper

Newspaper has mediation effect between education and depression.

```{r}
Npr.mod = '
  depre ~ a1* Newspaper +b1 *age + b2*gender +b3*education + b4* income
  Newspaper~ c1 *age + c2*gender +c3*education + c4* income
  Indirect1 := a1*c1
  Indirect2 := a1*c2
  Indirect3 := a1*c3
  Indirect4 := a1*c4
  age ~~ gender
  gender ~~ education
  education ~~ income
  age ~~ education
  age ~~ income
  gender ~~ income'
Npr.model = sem(Npr.mod, data = d,
               std.lv = TRUE , meanstructure = TRUE )

parameterestimates(Npr.model, boot.ci.type = "bca.simple", standardized = TRUE) %>% 
  kbl(.,booktab = TRUE) %>%
  kable_styling(latex_options = c("hold_position")) 

```

\newpage

## Information source mediation analysis

Information source related confusion has significant mediation effect between age and depression.

Information source related confusion has relatively weak significant mediation effect (p\<0.1) between income and depression.

Information source related certainty has relatively weak (p\<0.1) mediation effect between education and depression.

```{r}
## information source rename
d = d %>%
  dplyr:: mutate(certainty = Q17_1,
         overload = Q17_2,
         anxiety = Q17_3,
         confusion = Q17_4)
## all source assessment 
source.mod = '
  depre ~ a1* certainty +a2* overload + a3* anxiety + a4* confusion +b1 *age + b2*gender +b3*education + b4* income
  certainty ~ c1 *age + c2*gender +c3*education + c4* income
  overload ~ d1 *age + d2*gender +d3*education + d4* income
  anxiety ~  e1 *age + e2*gender +e3*education + e4* income
  confusion ~  f1 *age + f2*gender +f3*education + f4* income
  Indirect1 := a1*c1
  Indirect2 := a1*c2
  Indirect3 :=a1*c3
  Indirect4 :=a1*c4
  Indirect5 := a2*d1
  Indirect6 := a2*d2
  Indirect7 :=a2*d3
  Indirect8 :=a2*d4
  Indirect9 := a3*e1
  Indirect10 := a3*e2
  Indirect11 :=a3*e3
  Indirect12 :=a3*e4
  Indirect13 := a4*f1
  Indirect14:= a4*f2
  Indirect15 :=a4*f3
  Indirect16 :=a4*f4
  age ~~ gender
  gender ~~ education
  education ~~ income
  age ~~ education
  age ~~ income
  gender ~~ income'

sa.model = sem(source.mod, data = d,
             std.lv = TRUE , meanstructure = TRUE )
parameterestimates(sa.model, boot.ci.type = "bca.simple", standardized = TRUE) %>% 
  kbl(.,booktab = TRUE) %>%
  kable_styling(latex_options = c("hold_position")) 

```
